A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-15 papers/paper1/ms.tex
added some figures to the latex file
Started adding descriptions for the figures to the latex file

\usepackage[caption=false]{subfig}
\usepackage{censor}
\usepackage{booktabs}

@@

\subsection{Sample selection}
Our initial sample mirrors...
Hello!

@@

@@

>>>>

\usepackage[caption=false]{subfig}
\usepackage{censor}
\usepackage{booktabs}
\usepackage{graphicx}
\graphicspath{{./figures/}}

@@

\subsection{Sample selection}
Our initial sample mirrors...

@@

Using the rapid rotator sample, we compared the amplitudes of the TESS and Kepler missions. We created a mask that removes outliers exceeding predetermined limitations, as seen below.

  % Helpful resource on how to insert and align images
  % https://www.overleaf.com/learn/latex/Inserting_Images
  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{Comparison Between TESS and Kepler Amplitudes.png}
    \caption{Relationship between the calculated amplitudes of TESS and Kepler and how close they are to unity}
  \end{figure}

@@

Using the rapid rotator sample, we compared the rotational periods of both missions versus their amplitudes. This graph proves that our hypothesis from our proposal was correct. We estimate that the Kepler data is approximately 73 bigger that the TESS data (average amplitudes of 9353 versus 128, respectively).

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{Amplitude vs. Rotation for Kepler and TESS.png}
    \caption{Comparison between the rotational period vs. amplitude for both TESS and Kepler.}
  \end{figure}
